#---
#project: "Aletheia"
#title: EngineIII.Rmd
#output: html_notebook
#location: ~/Documents/In Process/ASM Final Project/Aletheia

#university: University of Colorado at Denver
#class: MATH 6388
#professor: Audrey Hendricks

#author: Kathleen Gatliffe
#date: 9 November 2018
---

# This is the main engine for the project
```{r}
setwd("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia")

library(stats)
library(dplyr)
library(hash)
library(ggplot2)
library(ReinforcementLearning)
#library(testthat)
#library(wesanderson)
```

#Load function file, parameters, color palettes.

```{r}
source("AllKFunctionsII.R")
source("Parameters.R")
source("AllKPalettes.R")
```

```{r}
load("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/PopulationN.7013.rda")
load("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/PopulationY.7013.0.1.rda")
```
##
#Run InitializePopulation.RMD Script to generate datasets with and without bias.

##
#No longer Tabula Rasa, the AI awakes. Sets actions (D: Detain, N: North, S: South, # W: West, E:East)

```{r}

Parameters<-LoadParameters()

Actions <- c("D", "N", "S", "W", "E")

AIMemory<-data.frame(matrix(vector(), 1, 4, dimnames=list(c(), c("State","Action","Reward","NextState"))),stringsAsFactors=F)
AIMemory$State=0
AIMemory$Action=0
AIMemory$Reward=0
AIMemory$NextState=0
Control<-list(alpha=Parameters$alpha,gamma=Parameters$gamma,epsilon=Parameters$epsilon)
```

#The town map matrix. The map contains an entry for every block. 

```{r}
TownMap=data.frame(matrix(vector(), 0, 18, dimnames=list(c(), c("X","Y","Flag","ID","Type","Vulnerable","VulnWeight","VulnTot","Criminal", "CrimWeight","CrimTot","Suspicious", "SuspWeight","SuspTot","DetainState","IgnoreHistory","DetainHistory","TypeW"))),stringsAsFactors=F)

TownMapLoc = data.frame(matrix(vector(), 1, 1, dimnames=list(c(), c( "X"))),stringsAsFactors=F)
for (i in 1:Parameters$cols){
  for(j in 1:Parameters$rows){
    TownMapLoc$X<-i
    TownMapLoc$Y<-j
    TownMapLoc$Flag<-0
    TownMapLoc$ID<-0
    TownMapLoc$Type<-0
    TownMapLoc$Vulnerable<-0
    TownMapLoc$VulnWeight<-0
    TownMapLoc$VulnTot<-0
    TownMapLoc$Criminal<-0
    TownMapLoc$CrimWeight<-0
    TownMapLoc$CrimTot<-0
    TownMapLoc$Suspicious<-0
    TownMapLoc$SuspWeight<-0
    TownMapLoc$SuspTot<-0
    TownMapLoc$DetainState<-sprintf("%03d",0)
    TownMapLoc$IgnoreHistory<-0
    TownMapLoc$DetainHistory<-0
    TownMapLoc$TypeW<-0    
  TownMap<-rbind(TownMap,TownMapLoc)
  }
}
```

#Seeding the Town Map. This routine adds the population to the map. The blocks that 
#are populated now contain the data on the person located there.

```{r}

if (Parameters$biasYN==0){Population<-PopulationN}
if (Parameters$biasYN==1){Population<-PopulationY}

PopCoord<-MakePop(Population, Parameters)
PopCoordY<-PopCoord
TownMap<- MakeMap(PopCoord, TownMap)
TownMap$Type<-factor(TownMap$Type)
TownMapY<-TownMap

for(i in 1:nrow(TownMapY))
{
for(j in 1:nrow(PopulationY)) 
{
  if (TownMapY$ID[i]==PopulationY$ID[j])
  {
    TownMapY$Suspicious[i]=PopulationY$Suspicious[j]
    TownMapY$SuspWeight[i]=PopulationY$SuspWeight[j]
    TownMapY$SuspTot[i]=PopulationY$SuspTot[j]
    TownMapY$DetainState[i]= PopulationY$DetainState[j] 
  }
}
}

for(i in 1:nrow(PopCoordY))
{
for(j in 1:nrow(PopulationY)) 
{
  if (PopCoordY$ID[i]==PopulationY$ID[j])
  {
    PopCoordY$Suspicious[i]=PopulationY$Suspicious[j]
    PopCoordY$SuspWeight[i]=PopulationY$SuspWeight[j]
    PopCoordY$SuspTot[i]=PopulationY$SuspTot[j]
    PopCoordY$DetainState[i]= PopulationY$DetainState[j] 
  }
}
}
iteration=1
save(PopCoord, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/PopCoord.",Parameters$seed,".",iteration,".rda"))
write.csv(PopulationY, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/PopCoord.",Parameters$seed,".",iteration,".csv"),row.names=FALSE)

save(TownMap, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/TownMap.",Parameters$seed,".",iteration,".rda"))
write.csv(TownMap, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/TownMap.",Parameters$seed,".",iteration,".csv"),row.names=FALSE)
save(TownMapY, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/TownMapY.",Parameters$seed,".",iteration,".rda"))
write.csv(TownMapY, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/TownMapY.",Parameters$seed,".",iteration,".csv"),row.names=FALSE)
```

# Setting up a complete list of states

```{r}
origin<-sample(nrow(TownMap),1,replace=T)
StateMatrixN<-AssignState(origin,TownMap,Parameters,Actions)
StateMatrixY<-AssignState(origin,TownMapY,Parameters,Actions)
#View(StateMatrixN)
#View(TownMap)
```


```{r}
StatesN=unique(StateMatrixN$State)
AIMemoryN<-sampleExperienceX(StateMatrixN,Parameters$N, MiniStateMatrix, StatesN, Actions, actionSelection = "random", control = Control, model = NULL)
save(AIMemoryN, file = paste0("AIMemory.",Parameters$seed,".",iteration,".rda"))

StatesY=unique(StateMatrixY$State)
AIMemoryY<-sampleExperienceX(StateMatrixY,Parameters$N, MiniStateMatrix, StatesY, Actions, actionSelection = "random", control = Control, model = NULL)
save(AIMemoryY, file = paste0("AIMemoryY.",Parameters$seed,".",iteration,".rda"))

save(StateMatrixN, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/StateMatrix.",Parameters$seed,".",iteration,".rda"))
save(StateMatrixY, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/StateMatrixY.",Parameters$seed,".",iteration,".rda"))
write.csv(StateMatrixY, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/StateMatrixY.",Parameters$seed,".",iteration,".csv"),row.names=TRUE)
write.csv(StateMatrixN, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/StateMatrix.",Parameters$seed,".",iteration,".csv"),row.names=TRUE)

```

# The initial model. This model is taken directly from a sample of states.
```{r}
TheModelN<-ReinforcementLearning(AIMemoryN, s="State", a="Action", r="Reward", s_new="NextState", control=Control)
TheModelY<-ReinforcementLearning(AIMemoryY, s="State", a="Action", r="Reward", s_new="NextState", control=Control)
```

#Saving the policy portion of the model.
```{r}
PolicyN<-(TheModelN$Policy)

save(PolicyN, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/PolicyN.",Parameters$seed,".",iteration,".rda"))
write.csv(PolicyN, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/PolicyN.",Parameters$seed,".",iteration,".csv"),row.names=TRUE)

PolicyY<-(TheModelY$Policy)

save(PolicyY, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/PolicyY.",Parameters$seed,".",iteration,".rda"))
write.csv(PolicyY, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/PolicyY.",Parameters$seed,".",iteration,".csv"),row.names=TRUE)
```

#Determining the Ideal Game (Not working as the model does not return a policy for all states)

```{r}

#source("ComparePolicy.R")
#xstep=TownMap$X[origin]
#ystep=TownMap$Y[origin]
#timestep=Parameters$daylength
#StateMatrix<-StateMatrixN
#PolicyN<- read.csv("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/PolicyN.7013.csv")
#PolicyY<- read.csv("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/PolicyY.7013.csv")
# GameHistoryN<-ComparePolicy(xstep,ystep,timestep,PolicyN, Parameters,StateMatrixN)
# GameHistoryY<-ComparePolicy(xstep,ystep,timestep,PolicyY, Parameters,StateMatrixY)
# View(GameHistoryN)
# View(GameHistoryY)
```

# Updating the data with new information

```{r eval=FALSE, include=FALSE}
data_newY <- sampleExperienceX(StateMatrixY,Parameters$N, env=MiniStateMatrix, states=StatesY, actions=Actions, 
                             model = TheModelY, actionSelection = "epsilon-greedy", 
                             control = Control)
data_newN <- sampleExperienceX(StateMatrixN,Parameters$N, env=MiniStateMatrix, states=StatesN, actions=Actions, 
                             model = TheModelN, actionSelection = "epsilon-greedy", 
                             control = Control)
```
Creating a new model using the initial model and the new data

```{r eval=FALSE, include=FALSE}
model_newN<-ReinforcementLearning(data_newN, s="State", a="Action", r="Reward", s_new="NextState", control=Control, model=model_newN)
model_newY<-ReinforcementLearning(data_newY, s="State", a="Action", r="Reward", s_new="NextState", control=Control, model=model_newY)

plot(model_newN)
plot(model_newY)

summary(model_newN)
summary(model_newY)

save(model_newN, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/model_newN.",Parameters$seed,".",iteration,".rda"))
write.csv(model_newN, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/model_newN.",Parameters$seed,".",iteration,".csv"),row.names=TRUE)

save(Model_newY, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/model_newY.",Parameters$seed,".",iteration,".rda"))
write.csv(model_newY, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/model_newY.",Parameters$seed,".",iteration,".csv"),row.names=TRUE)
```