#---
#project: "Aletheia"
#title: InitializePopulation.Rmd
#output: html_notebook
#location: ~/Documents/In Process/ASM Final Project/Aletheia

#university: University of Colorado at Denver
#class: MATH 6388
#professor: Audrey Hendricks

#author: Kathleen Gatliffe
#date: 9 November 2018
#---

# This file creates the population data file for the Aletheia project.

```{r}
setwd("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia")

library(stats)
library(dplyr)
library(hash)
library(ggplot2)
library(ReinforcementLearning)
library(testthat)
library(wesanderson)
```

# Load function file, parameters, color palettes.

```{r}
source("AllKFunctions.R")
source("Parameters.R")
source("AllKPalettes.R")
```

# Load parameters.

```{r}
Parameters<-LoadParameters()
```

# This is the population seeding routine.

```{r}

set.seed=(Parameters$seed)

PopulationN = data.frame(matrix(vector(), 0, 14, dimnames=list(c(), c("ID", "Type","Vulnerable","VulnWeight","VulnTot","Criminal","CrimWeight","CrimTot","Suspicious","SuspWeight","SuspTot","DetainState","IgnoreHistory","DetainHistory"))),stringsAsFactors=F)
Person = data.frame(matrix(vector(), 1, 14, dimnames=list(c(), c( "ID", "Type","Vulnerable","VulnWeight","VulnTot","Criminal","CrimWeight","CrimTot", "Suspicious","SuspWeight","SuspTot","DetainState","IgnoreHistory","DetainHistory"))),stringsAsFactors=F)
for (i in 1:Parameters$pop)
{
Person$ID <-i 
Person$Type <- sample(1:2, 1, replace=T,prob=c(1-Parameters$percgroup,Parameters$percgroup))
Person$Vulnerable<-sample(100,1,replace=T)/100
Person$VulnWeight <- 0
Person$VulnTot <-Person$Vulnerable+Person$VulnWeight
Person$Criminal <- rlnorm(1, log(5), log(1.25))/10
Person$CrimWeight <- 0
Person$CrimTot <-Person$Criminal+Person$CrimWeight
Person$Suspicious <- (Person$CrimTot+.5*Person$VulnTot+1+rlnorm(1, log(5), log(1.25)))/15
Person$SuspWeight <- 0
Person$SuspTot <-Person$Suspicious+Person$SuspWeight
roundedsusp<-round(Person$SuspTot*100)
Person$DetainState<-sprintf("%03d",roundedsusp)
Person$IgnoreHistory <- 0
Person$DetainHistory <- 0

if(Person$Type=="1"){Person$TypeW="Not Target"}
else {Person$TypeW="Target"}
PopulationN<-rbind(PopulationN,Person)

}

save(PopulationN, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/PopulationN.",Parameters$seed,".rda"))
write.csv(PopulationN, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/PopulationN.",Parameters$seed,".csv"),row.names=FALSE)
```

# Reweighting Suspicious. This chunk creates a version of population where the only 
#change is that type 2 is rated more suspicious.

```{r}
PopulationY<-PopulationN
  for (j in 1:Parameters$pop)
{
    if (PopulationY$Type[j]=="2")
PopulationY$Suspicious[j] <- PopulationY$Suspicious[j]*(1+Parameters$bias)
    Person$SuspWeight <- 0
PopulationY$SuspTot <-PopulationY$Suspicious+PopulationY$SuspWeight
roundedsusp<-round(PopulationY$SuspTot*100)
PopulationY$DetainState<-sprintf("%03d",roundedsusp)
  }

save(PopulationY, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/PopulationY.",Parameters$seed,".", Parameters$bias,".rda"))
write.csv(PopulationY, file = paste0("/Users/gatliffe/Documents/In Process/ASM Final Project/Aletheia/Iteration/PopulationY.",Parameters$seed,".", Parameters$bias,".csv"),row.names=FALSE)
```
